QCL: Added value of differential correlation

### 2012-01-10 inst/doc/article.Rnw
Updates to article

\begin{figure}[ht]
  \centerline{\includegraphics{QCL.pdf}}
  \caption{QCL mapping: The underlying hypothesis of QCL mapping. Seen here is a network of 3 phenotypes, in 
  which expression of P1, P2 and P3 is measured, and we want to infer the hidden relation between P1 
  and P2. In our model a genetic pertubation is causing P1 to change in expression showing a QTL at a marker. We expect variation 
  induced by P1 to transfer to P2, However (like in most biological systems) expression of P2 is tightly controlled, 
  and variation seen in phenotype 1 wil not induce a QTL in phenotype 2. However when we partition individuals based 
  on the genotype at the QTL marker of P1, we can make use of the correlation structure between P1 and P2. Allowing 
  us to infer the relationship between phenotype 1 and 2, when we see difference in correlation between P1A and P2A 
  and P1B and P2B. We don't observe this difference in correlation between P3 and P1, meaning there is no relation 
  between P1 and P3}
  \label{QCL_img}
\end{figure}

\begin{figure}[ht]
  \centering
<<permutation_scores, fig=TRUE, echo=FALSE, height=3.0>>=
op <- par(cex=0.5)
hist(ath.result,c(3,2,1))
op <- par(cex=1)
@ 
  \caption{QCL scores obtained during permutations (A. Thaliana) additional information obtained by QCL mapping, 
  which can be used to reconstruct the underlying genetic architecture.\label{fig:histPermAra}}
\end{figure}

\begin{figure}
  \centering
<<singletrait, fig=TRUE, echo=FALSE, height=3.0>>=
op <- par(cex=0.5)
plot(ath.result[[1]])
op <- par(cex=1)
@
  \caption{QCL profile (A. Thaliana, X3.Hydroxypropyl) transformed to LOD scores compared to the QTL profile of the same phenotype, We see an 
  additional significant peek for this phenotype (Between Marker 50 to 60) \label{fig:singletrait}}
\end{figure}

\begin{figure}
  \centering
<<singletraitLOD, fig=TRUE, echo=FALSE, height=6.0>>=
op <- par(cex=0.5)
QCLasLOD(ath.result[[1]], ath.result[[1]]$qtl)
op <- par(cex=1)
@ 
  \caption{QCL profile (A. Thaliana, X3.Hydroxypropyl) transformed to LOD scores. Shown is the likelyhood contribution of each of 
  the 24 metabolites to the QCL profile. \label{fig:singletraitLOD}}
\end{figure}

\begin{figure}[ht]
  \centering
<<p2mmatrix, fig=TRUE, echo=FALSE, height=3.0>>=
par(mar=c(3,8,1.1,1.1))
plot(ath.result, against="markers", do.grid=TRUE, grid.col="white")
@ 
  \caption{Phenotypes x Markers matrix (A. Thaliana) this is 'comparable' to a QTL scan on multiple traits.\label{fig:p2mmatrix}}
\end{figure}

\begin{figure}[ht]
  \centering
<<QTLmatrix, fig=TRUE, echo=FALSE, height=3.0>>=
par(mar=c(3,8,1.1,1.1))
QTLimage(ath.result, do.grid=TRUE, grid.col="white")
@
  \caption{Heatmap showing QTL scores for all 24 metabolities in A. Thaliana.\label{fig:QTLmatrix}}
\end{figure}

\begin{figure}[ht]
  \centering
<<p2pmatrix, fig=TRUE, echo=FALSE, height=3.0>>=
par(mar=c(3,8,1.1,1.1))
plot(ath.result, against="phenotypes", do.grid=TRUE, grid.col="white")
@ 
  \caption{Phenotypes x Phenotypes matrix (A. Thaliana) additional information obtained by QCL mapping, 
  which can be used to reconstruct the underlying genetic architecture.\label{fig:p2pmatrix}}
\end{figure}

\begin{figure}[ht]
  \centerline{\includegraphics{AraNet.pdf}}
  \caption{Reconstructed network for chain elongation in Arabidopsis Thaliana}
  \label{AraNet}
\end{figure}

>>>>

\begin{figure}[ht]
  \centerline{\includegraphics[height=7cm]{qcl.pdf}}
  \vspace{-15pt}
  \caption{{\scriptsize QCL mapping: We start by looking at a single genetic marker and dividing our populaiton into two groups.
  We start by choosing a phenotype (red), and use its expression to detect the red module (high correlation in gray genotype). 
  We see that something underlying our current marker in the gray genotype regulates the expression of red (but not blue)}}
  \vspace{-20pt}
  \label{fig:qcl}
\end{figure}

\begin{figure}[ht]
  \centerline{\includegraphics[height=6cm]{qcl_n.pdf}}
  \vspace{-15pt}
  \caption{{\scriptsize Reconstructed pathway location from gene expression data: Insight into the underlying (hidden) regulatory network 
  can be obtained when we look at the amount of expression showing the same switch. Depending on the amount of blue expressions 
  co-affected we can guestimate the location of the red expression inside the pathway}}
  \vspace{-20pt}
  \label{fig:qcl_n}
\end{figure}

\begin{figure}[ht]
  \centering
<<permutation_scores, fig=TRUE, echo=FALSE, height=3.0>>=
op <- par(cex=0.5)
hist(ath.result,c(3,2,1))
op <- par(cex=1)
@ 
  \caption{{\scriptsize QCL scores obtained during permutations (A. Thaliana) additional information obtained by QCL mapping, 
  which can be used to reconstruct the underlying genetic architecture. }}
  \label{fig:histPermAra}
\end{figure}

\begin{figure}
  \centering
<<singletrait, fig=TRUE, echo=FALSE, height=3.0>>=
op <- par(cex=0.5)
plot(ath.result[[1]])
op <- par(cex=1)
@
  \caption{{\scriptsize QCL profile (A. Thaliana, X3.Hydroxypropyl) transformed to LOD scores compared to the QTL profile of the same phenotype, We see an 
  additional significant peek for this phenotype (Between Marker 50 to 60) }}
  \label{fig:singletrait}
\end{figure}

\begin{figure}
  \centering
<<singletraitLOD, fig=TRUE, echo=FALSE, height=6.0>>=
op <- par(cex=0.5)
QCLasLOD(ath.result[[1]], ath.result[[1]]$qtl)
op <- par(cex=1)
@ 
  \caption{{\scriptsize QCL profile (A. Thaliana, X3.Hydroxypropyl) transformed to LOD scores. Shown is the likelyhood contribution of each of 
  the 24 metabolites to the QCL profile.}}
  \label{fig:singletraitLOD}
\end{figure}

\begin{figure}[ht]
  \centering
<<p2mmatrix, fig=TRUE, echo=FALSE, height=3.0>>=
par(mar=c(3,8,1.1,1.1))
plot(ath.result, against="markers", do.grid=TRUE, grid.col="white")
@ 
  \caption{{\scriptsize Phenotypes x Markers matrix (A. Thaliana) this is 'comparable' to a QTL scan on multiple traits.}}
  \label{fig:p2mmatrix}
\end{figure}

\begin{figure}[ht]
  \centering
<<QTLmatrix, fig=TRUE, echo=FALSE, height=3.0>>=
par(mar=c(3,8,1.1,1.1))
QTLimage(ath.result, do.grid=TRUE, grid.col="white")
@
  \caption{{\scriptsize Heatmap showing QTL scores for all 24 metabolities in A. Thaliana.}}
  \label{fig:QTLmatrix}
\end{figure}

\begin{figure}[ht]
  \centering
<<p2pmatrix, fig=TRUE, echo=FALSE, height=3.0>>=
par(mar=c(3,8,1.1,1.1))
plot(ath.result, against="phenotypes", do.grid=TRUE, grid.col="white")
@ 
  \caption{{\scriptsize Phenotypes x Phenotypes matrix (A. Thaliana) additional information obtained by QCL mapping, 
  which can be used to reconstruct the underlying genetic architecture}}
  \label{fig:p2pmatrix}
\end{figure}
